$\pi$ with leftovers: \\ a mechanisation in Agda

### 2020-05-08 paper/paper.tex
Comment on Pientka's work and further work on nonlinear pi calculus

>>>>

Based on contextual type theory \cite{Pientkaa, Pientka}, LINCX \cite{Georges2017} extends the linear logical framework LLF \cite{Cervesato1996} by internalising the notion of bindings and contexts.
The result is a meta-theory in which HOAS encodings with both linear and dependent types can be described.
The developer obtains for free an equational theory of substitution and decidable typechecking without having to encode context splits within the object language.

% Orchard
\cite{Orchard}

Further work on the mechanisation of the \picalc{} include \cite{Henry-Gerard1999, Honsell2001a, Bengtson2013, Despeyroux2000, Affeldt2008}, where the authors mechanise non-linear variations of the \picalc{}.
